An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
remove cache folder

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(knitcitations)
library(RefManageR)
knitr::opts_chunk$set(echo=FALSE, 
                      message=FALSE, 
                      warning=FALSE, 
                      kfigr.link=TRUE, 
                      kfigr.prefix=TRUE, 
                      cache=TRUE, 
                      fig.cap=TRUE)

>>>>

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
library(knitcitations)
library(RefManageR)
knitr::opts_chunk$set(echo=FALSE, 
                      message=FALSE, 
                      warning=FALSE, 
                      kfigr.link=TRUE, 
                      kfigr.prefix=TRUE, 
                      cache=TRUE, 
                      fig.cap=TRUE, comment = FALSE)
